Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
Abstract

The term {\em stack safety} is used for a variety of compiler,
run-time, and hardware mechanisms for protecting stack memory. Unlike
``the heap,'' the hardware stack does not correspond to a single
high-level language concept: different compilers use it in different
ways to support procedural and functional abstraction mechanisms from
a wide range of languages.  This protean nature makes it difficult to
nail down what it means to correctly enforce stack safety.

@@

The hardware stack interacts with a large number of language features,
some of which are typically excluded from discussions of stack
safety. Our properties go further than previous proposals,
supporting caller- and callee-saved registers, arguments passed on the
stack, \ifexceptions tail-call elimination, and exceptions.  \else and
tail-call elimination. \fi They are modular by design so that they
can be further extended to other features.

@@

      ~ \stackrel{\mathtt{a0}}{\pubbox\pubbox} ~ \stackrel{\mathtt{a1}}{\freebox\freebox}

>>>>

The term {\em stack safety} is used for a variety of compiler,
run-time, and hardware mechanisms for protecting stack memory. Unlike
``the heap,'' the ISA-level stack does not correspond to a single
high-level language concept: different compilers use it in different
ways to support procedural and functional abstraction mechanisms from
a wide range of languages.  This protean nature makes it difficult to
nail down what it means to correctly enforce stack safety.

@@

% The stack plays a central role in realizing large number of
% high-level language features, some of which are typically excluded
% from discussions of stack safety. 
Our properties go further than previous formal definitions of stack
safety, supporting caller- and callee-saved registers, arguments
passed on the stack, \ifexceptions tail-call elimination, and
exceptions.  \else and tail-call elimination. \fi 
% \bcp{Out of all of
%   these, only exceptions are high-level language features!}
They are modular by design so that they can be further extended to
other features.

@@

      ~ \stackrel{\mathtt{a0}}{\objbox\objbox} ~ \stackrel{\mathtt{a1}}{\freebox\freebox}
